Programs Performance Analysis Toolkit

### 2013-10-08 keynote/Keynote.tex
Finish the architecture drawing

>>>>

\section{Implementation}

\begin{frame}[fragile]
\frametitle{Architecture of \textit{Adaptor} Framework}

\begin{center}
\begin{asy}
	unitsize(0.5mm);

	struct Rectangle {
		pair lb;
		pair rt;
		Label l;
		pen border;
		pen fill;

		void operator init(pair lb, pair rt, Label l="", pen border = black, pen fill = white)
		{
			this.lb = lb;
			this.rt = rt;
			this.l = l;
			this.border = border;
			this.fill = fill;
		}
	}

	struct Block {
		Rectangle rect;
		Rectangle[] childs;
		Label label;

		void operator init(pair lb, pair rt, Label l="", pen border = black, pen fill = white, Rectangle[] childs)
		{
			rect.operator init(lb, rt, "", border, fill);
			this.childs = childs;
			this.label = l;
		}
	}

	void draw(Rectangle r)
	{
		path p = r.lb--(r.lb.x, r.rt.y)--r.rt--(r.rt.x, r.lb.y)--cycle;
		fill(p, r.fill);
		label(r.l, ( r.lb.x + (r.rt.x - r.lb.x) / 2 , 
		             r.lb.y + (r.rt.y - r.lb.y) / 2 ));
		draw	(p, r.border);
	}

	void draw(Block s)
	{
		draw(s.rect);
		label(s.label, ( s.rect.lb.x + (s.rect.rt.x - s.rect.lb.x) / 2 , 
		                 s.rect.rt.y - 5 ));
		for (Rectangle r : s.childs) {
			draw(r);
		}
	}

	Rectangle[] rects1 = {
		Rectangle((5,5), (145,15), Label("Data views"), black, lightblue)
	};
	draw(Block((0,0), (150,30), Label("Database server"), black, lightgreen, rects1));

	Rectangle[] rects2 = {
		Rectangle((5,-35), (145,-25), Label("Database interaction module"), black, lightblue),
		Rectangle((5,-50), (145,-40), Label("Program building module"), black, lightblue),
		Rectangle((5,-65), (145,-55), Label("Experimentation module"), black, lightblue),
		Rectangle((5,-80), (145,-70), Label("Information retrieval module"), black, lightblue),
		Rectangle((5,-95), (145,-85), Label("Information processing module"), black, lightblue)
	};
	draw(Block((0,-100), (150,-10), Label("Client"), black, lightgreen, rects2));

\end{asy}
\end{center}
\end{frame}
